Probabilistic Symbol Encoding for \\Convolutional Associative Memories

### 2016-12-19 papers/hrr-paper/paper.tex

		\begin{figure}[th!]
			\begin{subfigure}{0.45\columnwidth}
				\center
				\includegraphics[width=1\columnwidth]{img/gaussianbar.png}
				\caption{Gaussian probability distribution for raw input value}
				\label{fig:gaussianbar}
			\end{subfigure}
			\begin{subfigure}{0.54\columnwidth}
				\center
				\includegraphics[width=1\columnwidth]{img/gaussianbarperm.png}
				\caption{Probabilistic symbolic encoding suitable for HRR after permutation
				}
				\label{fig:gaussianbarperm}
			\end{subfigure}	
		\caption{Sensory input encoding of target object position in the visual field at two successive points in time. Left graph shows original encodings for two adjacent values and right graph shows permuted encodings. It can be seen that semantically close input values result in similar HRR encodings.}
		\label{gaussian}
		\end{figure}

>>>>

		\begin{figure}[th!]
			\begin{subfigure}{0.45\columnwidth}
				\center
				\includegraphics[width=1\columnwidth]{img/gaussianbar.png}
				\caption{Gaussian probability distribution for raw input value}
				\label{fig:gaussianbar}
			\end{subfigure}
			\begin{subfigure}{0.54\columnwidth}
				\center
				\includegraphics[width=1\columnwidth]{img/gaussianbarperm.png}
				\caption{Probabilistic symbolic encoding suitable for HRR after permutation
				}
				\label{fig:gaussianbarperm}
			\end{subfigure}	
		\caption{Sensory input encoding of target object position in the visual field at two successive points in time. Left graph shows original encodings for two adjacent values and right graph shows permuted encodings. It can be seen that semantically close input values result in similar HRR encodings.}
		\label{fig:gaussian}
		\end{figure}

	In our experiment we have extended the detection of light to a position along the visual field, reduced to the X-axis, rather than just binary statements like "light is visible to the left". To visualize the difference chart \ref{fig:gaussianbar} shows the position of light for two consecutive time steps. The value $0$ represents the far left corner of the sensor, and $1$ the far right one. The chart can be viewed as a (normalized) probability of light being at a certain position, and both cases show it being somewhere right of the center. Chart \ref{fig:gaussianbarperm} shows what the Gaussian distributions look like when they are permuted. This shape of theirs is then used as a symbol. Concretely, instead of encoding a random symbol for "light\_left" we encode a scalar representing the position of light along the visual field and bind it with the rest of the controller components. Accordingly, when running the experiment, once the light reaches a position encoded in the controller it will issue new commands to the vehicle.
